---
title: "Create Subsampled Data"
output: html_notebook
---
```{r}
library("dplyr")
library("readr")
library("stringr")
```

This notebook creates a subsampled dataset that we can use for experimentation.
We restrict attention to sentinel 2 images and their labels.

This subsamples using the following strategy,
* Choose 20 regions at random.
* Pick 150 patches at random from each.

This will give us 3,000 patches for experimentation.

```{r}
scene_dirs <- c(
  list.dirs("/Volumes/ksankaran/Sen12MS/ROIs1158_spring",  recursive = F),
  list.dirs("/Volumes/ksankaran/Sen12MS/ROIs1868_summer",  recursive = F),
  list.dirs("/Volumes/ksankaran/Sen12MS/ROIs1970_fall",  recursive = F),
  list.dirs("/Volumes/ksankaran/Sen12MS/ROIs2017_winter",  recursive = F)
)
  
s2_dirs <- scene_dirs[grepl("s2_", scene_dirs)]
```

This creates the subsample.

```{r}
n <- 20
n_per_scene <- 150

s2_dirs <- sample(s2_dirs, n)
scenes <- list()
for (i in seq_along(s2_dirs)) {
  scenes[[i]] <- sample(list.files(s2_dirs[1], "*tif", full.names = TRUE), n_per_scene)
}
```

Next, we extract metadata (pathnames, seasons) associated with this subsample.

```{r}
parse_path <- function(path) {
  comps <- strsplit(basename(path), "_|\\.")[[1]]
  data.frame(
    "image_path" = path,
    "image_basename" = basename(path),
    "roi" = comps[1],
    "season" = comps[2],
    "scene" = comps[4],
    "patch" = comps[5]
  )
}

metadata <- lapply(unlist(scenes), parse_path)
metadata <- do.call(rbind, metadata)
```

To get the corresponding labels, we just replace `s2` with `lc` in all the
paths.

```{r}
metadata <- metadata %>%
  mutate(
    label_path = str_replace_all(image_path, "s2", "lc"),
    label_basename = str_replace_all(image_basename, "s2", "lc")
  ) %>%
  select(image_basename, label_basename, roi, season, scene, patch, image_path, label_path)
```

Now we can copy those files and write the metadata.

```{r}
target_dir <- "/Volumes/ksankaran/sen12ms_subsample/"
dir.create(target_dir)
dir.create(file.path(target_dir, "images"))
dir.create(file.path(target_dir, "labels"))

for (i in seq_along(metadata$image_path)) {
  image_path <- file.path(target_dir, "images", metadata$image_basename[i])
  file.copy(metadata$image_path[i], image_path)
  
  label_path <- file.path(target_dir, "labels", metadata$label_basename[i])
  file.copy(metadata$label_path[i], label_path)
}

write_csv(metadata, file.path(target_dir, "metadata.csv"))
```
